Adaptability of ecophysiological traits define how plant lineages make a living in shaded environments 

### 2019-03-11 manuscript/manuscript.Rmd
new plots

```{r global data/sourcing, echo=FALSE, message=FALSE, warning=FALSE}
# Set Flag to include figures in text or not.
includeFigs <- FALSE
```

@@

# Tables {.unnumbered}
**Table 1**.

@@

```{r allometry, fig.width=7, fig.height=7, echo=FALSE,  dev="png", dpi=600,eval=includeFigs}
source("master_scripts/pca_plot.R")
```  
**Figure 1**. Redundancy analysis of measured functional traits across con-occuring angiosperms and fern species in open and shaded habitats. With the 12 measured variables, number% of the trait variation was accounted for in two dimensions. Variables include net photosynthesis (A~n~), stomatal conductance (g~s~), instantaneous water use efficiency (WUE), stomatal density (SD), the light compensation point (LCP), quantum yield ($$\phi$$), dark respiration (R~d~), foliar nitrogen (N) and phosphorus (P) content, the leaf carbon to nitrogen ratio (C:N) and the leaf nitrogen to phosphorus ratio (N:P).

@@

```{r allometry, fig.width=7, fig.height=7, echo=FALSE,  dev="png", dpi=600,eval=includeFigs}
source("master_scripts/pca_canopy.R")
```  
**Figure 2**. Redundancy analysis of measured functional traits across con-occuring angiosperms fern and lycopyte species in shaded habitats.

>>>>

```{r global data/sourcing, echo=FALSE, message=FALSE, warning=FALSE}
# Set Flag to include figures in text or not.
includeFigs <- TRUE
```

@@

# Tables {.unnumbered}

**Table 1**. Species list.

```{r speciestable, echo=FALSE,warning=FALSE, message=FALSE}}
library(pixiedust)
speciestab <- read.csv("raw_data/species_list.csv")

dust(speciestab[1:4])%>%
  sprinkle_colnames("Species", "Plant Lineage", "Collection Site", 
                    "Canopy") %>%
  sprinkle(rows= 1, part="head",bold=TRUE)%>%
  sprinkle_print_method("markdown")
```

@@

```{r pca1, fig.width=7, fig.height=7, echo=FALSE,  dev="png", dpi=600,eval=includeFigs,warning=FALSE, message=FALSE}
source("master_scripts/pca_plot.R")
```  
**Figure 1**. Redundancy analysis of measured functional traits across con-occuring angiosperms and fern species in open and shaded habitats. With the 12 measured variables, number% of the trait variation was accounted for in two dimensions. Variables include net photosynthesis (A~n~), stomatal conductance (g~s~), instantaneous water use efficiency (WUE), stomatal density (SD), the light compensation point (LCP), quantum yield ($\phi$), dark respiration (R~d~), foliar nitrogen (N) and phosphorus (P) content, the leaf carbon to nitrogen ratio (C:N) and the leaf nitrogen to phosphorus ratio (N:P).

@@

```{r pca2, fig.width=7, fig.height=7, echo=FALSE,  dev="png", dpi=600,eval=includeFigs,warning=FALSE, message=FALSE}
source("master_scripts/pca_canopy.R")
```  
**Figure 2**. Redundancy analysis of measured functional traits across con-occuring angiosperms fern and lycopyte species in shaded habitats.

```{r interaction, fig.width=7, fig.height=7, echo=FALSE,  dev="png", dpi=600,eval=includeFigs, warning=FALSE, message=FALSE}
source("master_scripts/interaction_plots.R")
```  
**Figure 3**. Differences in mean physiological traits between co-occuring angiosperms and fern species in open light and closed habitats.

```{r lyco, fig.width=7, fig.height=7, echo=FALSE,  dev="png", dpi=600,eval=includeFigs, warning=FALSE, message=FALSE}
source("master_scripts/lycophytes_plot.R")
```  
**Figure 4**. Differences in mean physiological traits between lycophytes species that are constrained to only shade habitats and ferns and angiosperms.

```{r seed, fig.width=7, fig.height=7, echo=FALSE,  dev="png", dpi=600,eval=includeFigs, warning=FALSE, message=FALSE}
source("master_scripts/seed_nonseed_plots.R")
```  
**Figure 5**. Differences in mean physiological traits between co-occuring seed (angiosperms) and non-seed plant species (ferns + lycophytes) in shade habitats.
